\chapter{Coordinators}\label{sec:coordinators}

Coordinators are responsible for upholding the values of the Collective as defined in Article III of the Constitution. They are elected twice a year as per Bylaw~\ref{sec:elections}, and each position is open at only one of those two elections.

If they fail to uphold the Collective's values, a warning may be issued by a majority vote of the coordinators. Three warnings cause the coordinator to be removed from their position.

A coordinator may voluntarially vacate their position by notifying the other coordinators.

Vacant positions may be temporarily filled by any member through a majority vote of the current coordinators. Temporary coordinators abide by the same rules and guidelines as other coordinators.

There are no limits on the number of terms a coordinator may serve.

What follows is a complete list of coordinator positions for the Collective. The election in which the position is open is indicated as ``Summer'' or ``Winter''.

\section[Steward]{Steward (Summer)}\label{sec:steward}
Responsible for long term vision, Collective community, and managing coordinators.

\section[Operations]{Operations (Winter)}\label{sec:operations}
Responsible for internal affairs, event management, and assisting coordinators.

\section[Treasurer]{Treasurer (Summer)}\label{sec:treasurer}
Responsible for budgeting, accounting, taxes.

\section[Fundraising]{Fundraising (Winter)}\label{sec:fundraising}
Responsible for pursuing grants, donations, and partners.

\section[Librarian]{Librarian (Summer)}\label{sec:librarian}
Responsible for organizing Collective information, skills, and resources.

\section[Historian]{Historian (Winter)}\label{sec:historian}
Responsible for running general meeting, taking attendance, and recording meeting notes.

\section[Diversity and Accessibility]{Diversity and Accessibility (Summer)}\label{sec:accessability}
Responsible for working to improve access and responding to any related issues, internal or external.

\section[Publicist]{Publicist (Winter)}\label{sec:publicist}
Responsible for public communication, managing the contact list, and ensuring transparency.
